%%% Seznam použité literatury je zpracován podle platných standardù. Povinnou citaèní
%%% normou pro bakaláøskou práci je ISO 690. Jména èasopisù lze uvádìt zkrácenì, ale jen
%%% v kodifikované podobì. Všechny použité zdroje a prameny musí být øádnì citovány.

%\def\bibname{Seznam použité literatury}
\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{\bibname}

\bibitem{Aimsun}
{\itshape Aimsun 7 Dynamic Simulators User’s Manual}. TSS-Transport Simulation Systems, 2012. 
%
\bibitem{Balci}
BALCI, Osman. Verification validation and accreditation of simulation models. In: \textit{Proceedings of the 29th conference on Winter simulation.} IEEE Computer Society, 1997. p. 135-141.
%
\bibitem{SUMO}
BEHRISCH, Michael, Laura BIEKER, Jakob ERDMANN a Daniel KRAJZEWICZ. SUMO - Simulation of Urban MObility - an Overview. In: \textit{ThinkMind (TM).} Barcelona: IARIA, 2011, s. 55-60. Dostupné také z: \url{http://sumo.dlr.de/pdf/simul_2011_3_40_50150.pdf}
%
\bibitem{Brackstone}
BRACKSTONE, Mark a Mike MCDONALD. Car-following: a historical review. \textit{Transportation Research Part F: Traffic Psychology and Behaviour}, 1999, 2.4: 181-196. Dostupné také z: \url{http://www.researchgate.net/profile/Mark_Brackstone/publication/222495203_Car-following_a_historical_review/links/542002a50cf241a65a1af53a.pdf}
%
\bibitem{Brockfeld}
BROCKFELD, Elmar, Reinhart D. KÜHNE a Peter WAGNER. Calibration and validation of microscopic traffic flow models. \textit{Transportation Research Record: Journal of the Transportation Research Board}. 2004, \textbf{1876}(1): 62-70. Dostupné také z: \url{http://core.ac.uk/download/pdf/11091639.pdf}
%
%\bibitem{Garcia}
%Garcia A, {\itshape Numerical methods for physics}, Addison-Wesley, 1999
%
\bibitem{CalibrationWWW}
Model Calibration. \textit{WisDOT Information Wiki} [online]. 2009 [cit. 2015-04-23]. Dostupné z: \url{http://www.wisdot.info/microsimulation/index.php?title=Model_Calibration}
%
\bibitem{Doxygen}
SUMO Documentation. SUMO - Simulation of Urban MObility [online]. 2001 [cit. 2015-05-23]. Dostupné z: \url{http://www.sumo.dlr.de/doxygen/index.html}
%
\bibitem{Feldman}
FELDMAN, Olga. The GEH Measure and Quality of the Highway Assignment Models. In: \textit{European Transport Conference 2012} [online]. 2012 [cit. 2015-05-23]. Dostupné z: \url{http://www.researchgate.net/profile/Olga_Feldman2/publication/263140653_THE_GEH_MEASURE_AND_QUALITY_OF_THE_HIGHWAY_ASSIGNMENT_MODELS/links/00b4953a02a66492fe000000.pdf}
%
\bibitem{Gipps}
GIPPS, Peter G. A behavioural car-following model for computer simulation. \textit{Transportation Research Part B: Methodological.} 1981, \textbf{15}(2): 105-111. Dostupné také z: \url{http://turing.iimas.unam.mx/sos/sites/default/files/Gipps_ABehaviouralCarFollowingModel.pdf}
%
\bibitem{GNUplot}
GNUplot [online]. 2011 [cit. 2015-05-27]. Dostupné z: \url{http://www.gnuplot.info/}
%
\bibitem{Google}
Mapy Google. {\itshape Mapy Google} [online]. 2015 [cit. 2015-05-20]. Dostupné z: \url{https://www.google.cz/maps}
%
\bibitem{Higgs}
HIGGS, Bryan, Montasir M. ABBAS a Alejandra MEDINA. \textit{Analysis of the Wiedemann Car Following Model over Different Speeds using Naturalistic Data} [online]. 2011 [cit. 2015-05-23]. Dostupné z: \url{http://onlinepubs.trb.org/onlinepubs/conferences/2011/RSS/3/Higgs,B.pdf}
%
\bibitem{Jmatio}
JMATIO. JMatIO - Matlab's MAT-file I/O in JAVA - File Exchange - MATLAB Central [online]. 2013 [cit. 2015-05-27]. Dostupné z: \url{http://www.mathworks.com/matlabcentral/fileexchange/10759-jmatio-matlab-s-mat-file-i-o-in-java}
%
\bibitem{Kanagaraj}
KANAGARAJ, Venkatesan, Gowri ASAITHAMBI, C.H. Naveen KUMAR, Karthik K. SRINIVASAN a R. SIVANANDAN. Evaluation of Different Vehicle Following Models Under Mixed Traffic Conditions. In: \textit{Procedia - Social and Behavioral Sciences.} Amsterdam: Elsevier, 2013, s. 390-401. DOI: 10.1016/j.sbspro.2013.11.132. ISSN 18770428. Dostupné také z: \url{http://linkinghub.elsevier.com/retrieve/pii/S1877042813045230}
%
\bibitem{Kelton}
KELTON, David a Averill LAW. {\itshape Simulation modeling and analysis}. New York: McGraw-Hill, 1991. 
%
\bibitem{Kleijnen}
KLEIJNEN, Jack P.C. Statistical validation of simulation models. In: \textit{European Journal of Operational Research.} Amsterdam: Elsevier, 1995, s. 21-34. DOI: 10.1016/0377-2217(95)00132-a.
%
\bibitem{Krauss}
KRAUSS, Stefan. \textit{Microscopic Modeling of Traffic Flow: Investigation of Collision Free Vehicle Dynamics.} Köln, 1998. PhD. Thesis. Universität Köln.
%
\bibitem{May}
MAY, Adolf D. \textit{Traffic flow fundamentals.} Upper Saddle River: Prentice Hall, 1990, xi, 464 s. ISBN 01-392-6072-2.
%
\bibitem{Newell}
NEWELL, G. F. A simplified car-following theory: a lower order model. \textit{Transportation Research Part B: Methodological}. Amsterdam: Elsevier, 2002, \textbf{36}(3): 195-205.
%
\bibitem{Pavlik}
PAVLÍK, Jiøí. \textit{Aplikovaná statistika.} Praha: Vysoká škola chemicko-technologická, 2005, 172 s. ISBN 80-708-0569-2.

\bibitem{Pidd}
PIDD, Michael. \textit{Computer simulation in management science.} New York: Wiley, 1984, xiv, 237 p. ISBN 04-719-0281-0.
%
\bibitem{Song}
SONG, Jie, Yi WU, Zhexin XU a Xiao LIN. \textit{Research on car-following model based on SUMO.} The 7th IEEE/International Conference on Advanced Infocomm Technology [online]. 2014 [cit. 2015-05-23]. DOI: 10.1109/icait.2014.7019528.

\bibitem{SUMOWiki}
SUMO - Wiki. SUMO [online]. 2013 [cit. 2015-05-27]. Dostupné z: \url{http://sumo.dlr.de/wiki/Main_Page}
%
\bibitem{Treiber}
TREIBER, Martin, Ansgar HENNECKE a Dirk HELBING. \textit{Congested traffic states in empirical observations and microscopic simulations.} Physical Review E. 2000, \textbf{62}(2): 1805-1824. DOI: 10.1103/physreve.62.1805.
%
\bibitem{TreiberWWW}
TREIBER, Martin. \textit{Microsimulation of Road Traffic Flow} [online]. 2011 [cit. 2015-05-23]. Dostupné z: \url{www.traffic-simulation.de}

\bibitem{Vanis}
VANIŠ, Miroslav. \textit{Matematické modelování vybraných problémù v dopravì v jazyce Java}. Praha, 2013. bakaláøská práce. FD ÈVUT.
%
\bibitem{Willmott}
WILLMOTT, CJ a K MATSUURA. Advantages of the mean absolute error (MAE) over the root mean square error (RMSE) in assessing average model performance. \textit{Climate Research.} 2005, \textbf{30}(1): 79-82. DOI: 10.3354/cr030079.
%
\end{thebibliography}
